---
title: "tutorial"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(package.v1)
library(car)
library(bench)
library(microbenchmark)
```

## Introduction

This package focuses on linear regression calculation. With it, you can do model fitting, prediction, general linear hypothesis test, and residual calculations. There are six main functions in this package, which are `linear_model()`, `predict_mock()`, `GLH()`, `residuals()`, `dffit()`, and `Cooks()`.

Here, we use the built-in toy data set, `Davis`, from package `car` to demonstrate the usages of each function.

## Toy Dataset

Load in data set `Davis`.

```{r}
data <- Davis
head(data)
```

## Fit model

Say we are interested in studying students' weight adjusted for sex, height, repwt. Theoretically, our model is: $Weight = \beta_0 + \beta_1sex + \beta_2height + \beta_3repwt + \epsilon$ with $\epsilon \sim N(0,\sigma^2)$

First, we use self-defined model 'linear_model'

```{r}
mod <- linear_model(weight ~ repwt + height + sex, data = data)
```

Now, we compare it with original `lm` function

```{r}
mod2 <- lm(weight ~ repwt + height + sex, data = data)
summary(mod2)
```

### Correctness

Now compare two models using `all.equal` function.

```{r}
# coefficients
all.equal(as.vector(mod$Coefficients), as.vector(mod2$coefficients))

# standard error
all.equal(as.vector(mod$s.e), as.vector(summary(mod2)$coefficients[,2]))

# t value
all.equal(as.vector(mod$t_value), as.vector(summary(mod2)$coefficients[,3]))

# p value
all.equal(as.vector(mod$p_value), as.vector(summary(mod2)$coefficients[,4]))

# r square
all.equal(mod$R2[[1]], summary(mod2)$r.squared)

# adjusted r square
all.equal(mod$R2[[2]], summary(mod2)$adj.r.squared)
```

### Efficiency

```{r, results = FALSE}
compare =  bench::mark(as.vector(linear_model(weight ~ repwt + height + sex, data = data)$Coefficients), as.vector(lm(weight ~ repwt + height + sex, data = data)$coefficients))
res <- microbenchmark::microbenchmark(as.vector(linear_model(weight ~ repwt + height + sex, data = data)$Coefficients), as.vector(lm(weight ~ repwt + height + sex, data = data)$coefficients))
```

```{r, fig.asp = 0.8, fig.width = 9}
print(compare)
plot(res)
```


## Prediction

I manually generate 5 new observations.

```{r}
newobs <- data.frame("repwt" = c(50, 70, 70, 85, 63),
                     "height" = c(165, 189, 178, 150, 180),
                     "sex" = c('F', 'M', 'M', 'F', 'F'))
```

Again, I use self-defined function first

```{r}
predict_mock(mod, newobs)
```

The results given by R function:

```{r}
predict(mod2, newobs)
```

### Correctness

```{r}
all.equal(as.vector(predict_mock(mod, newobs)), as.vector(predict(mod2, newobs)))
```

### Efficiency

```{r, fig.asp = 0.8, fig.width = 9}
bench::mark(as.vector(predict_mock(mod, newobs)), as.vector(predict(mod2, newobs)))
plot(microbenchmark::microbenchmark(as.vector(predict_mock(mod, newobs)), as.vector(predict(mod2, newobs))))
```


## General Linear Hypothesis test

I will test following hypotheses

$H_0: \beta_{repwt} + 2*\beta_{weight} = 0 \space and \space \beta_{sex} = 0$

$H_1: not \space H_0$

```{r}
#Corresponding T matrix
(T = matrix(c(0,0,1,0,2,0,0,1), nrow = 2))
```

Results provided by self-defined function

```{r}
GLH(mod, T)
```

Results from `linearHypothesis` function in package `car`.

```{r}
linearHypothesis(mod2, T)
```

### Correctness

```{r}
all.equal(GLH(mod, T)[[1]], linearHypothesis(mod2, T)[2,5])
```

### Efficiency

```{r, fig.asp = 0.8, fig.width = 9}
bench::mark(GLH(mod, T)[[1]], linearHypothesis(mod2, T)[2,5])
plot(microbenchmark::microbenchmark(GLH(mod, T)[[1]], linearHypothesis(mod2, T)[2,5]))
```


## Residual Calculation

The results of implemented function are presented first.

```{r}
res <- residuals(mod)
head(res)
```

### Correctness

```{r}
# unstandardized residuals
all.equal(as.vector(res$residuals), as.vector(mod2$residuals))

# standardized residuals
all.equal(as.vector(res$standardized.residuals), as.vector(mod2$residuals/summary(mod2)$sigma))

# internal
all.equal(as.vector(res$internal.studentize), as.vector(rstandard(mod2)))

# external
all.equal(as.vector(res$external.studentize), as.vector(rstudent(mod2)))
```

### Efficiency


```{r}
origin <- function(mod) {
  results <- data.frame("residuals" = as.vector(mod$residuals),
                        "standardized.residuals" = as.vector(mod$residuals/summary(mod)$sigma),
                        "internal.studentize" = as.vector(rstandard(mod)),
                        "external.studentize" = as.vector(rstudent(mod)))
  
  return(results)
}
```

```{r, fig.asp = 0.8, fig.width = 9}
bench::mark(residuals(mod), origin(mod2))
plot(microbenchmark::microbenchmark(residuals(mod), origin(mod2)))
```

## DFFIT Calculation

The implemented function's results are presented first

```{r}
dffit(mod)[1:10]
```

Below are results of function `dffits` in `stats` package.

```{r}
stats::dffits(mod2)[1:10]
```

### Correctness

```{r}
all.equal(as.vector(dffit(mod)), as.vector(dffits(mod2)))
```

### Efficiency

```{r, fig.asp = 0.8, fig.width = 9}
bench::mark(as.vector(dffit(mod)), as.vector(dffits(mod2)))
plot(microbenchmark::microbenchmark(as.vector(dffit(mod)), as.vector(dffits(mod2))))
```


## Cook's distance

Still self-defined function are present first

```{r}
Cooks(mod)[1:10]

```

```{r}
stats::cooks.distance(mod2)[1:10]
```

### Correctness

```{r}
all.equal(as.vector(Cooks(mod)), as.vector(cooks.distance(mod2)))
```

### Efficiency

```{r, fig.asp = 0.8, fig.width = 9}
bench::mark(as.vector(Cooks(mod)), as.vector(cooks.distance(mod2)))
plot(microbenchmark::microbenchmark(as.vector(Cooks(mod)), as.vector(cooks.distance(mod2))))
```


