---
title: "tutorial"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(package.v1)
```

# Introduction

This package focus on linear regression calculation. With it, you can do model fitting, prediction, general linear hypothesis test, and residual calculations. There are four main functions in this package, which are `linear_model()`, `predict_mock()`, `GLH()`, and `residuals()`.

Here, we use the built-in toy data set, `Davis`, to demonstrate the usages of each function.

# Toy Dataset

Load in data set `Davis`.

```{r}
data <- Davis
head(data)
```

# Fit model

Say we are interested in study students' weight adjusted for sex, height, repwt. Theoretically, our model is: $Weight = \beta_0 + \beta_1sex + \beta_2height + \beta_3repwt + \epsilon$ with $\epsilon \sim N(0,\sigma^2)$

First, we use self-defined model 'linear_model'

```{r}
mod <- linear_model(weight ~ repwt + height + sex, data = data)
```

Now, we compare it with original `lm` function

```{r}
mod2 <- lm(weight ~ repwt + height + sex, data = data)
summary(mod2)
```







